Total Score

### 2023-02-03 src/MSAtotal_scores.Rmd
calculated total score w finalized weights

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_owen = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score),
         score_og_weights_EAL = cbsa
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$total_score_owen[i] = weighted.mean(cbsa_data, criteria_weights_owen)
}

##### original weights with EAL score

for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i] ## EAL score
                  )
  criteria_all$score_og_weights_EAL[i] = weighted.mean(cbsa_data, criteria_weights_owen)
}

@@

```{r student weights}
# weight criteria for students
criteria_weights_students <- c(0.21, 0.0, 0.12, 0.17, 0.16, 0.17, 0.17)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa) #this is just a place holder

@@

@@

```{r climate risk weighted 50 and other 0.1}
# weight criteria for Owen
weights_climate50 <- c(0.1, 0.1, 0.1, 0.1, 0.0, 0.1, 0.50)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50 = cbsa) #this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50[i] = weighted.mean(cbsa_data, weights_climate50)
}

```{r climate risk 40 }
# weight criteria for Owen
weights_climate40 <- c(0.15, 0.1, 0.15, 0.1, 0.0, 0.1, 0.40)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate40 = cbsa) #this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate40[i] = weighted.mean(cbsa_data, weights_climate40)
}
```

```{r climate risk 50 and proportional weights for others}

@@

```{r climate risk 35 and Jan 31 weights from owen}

@@

criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk,
         climate_EAL_risk = inverted_n_eal_score) %>% 
  mutate_if(is.numeric, ~round(., 5))

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "scores+EAL_2_2_23")
```

```{r data viz}

>>>>

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_owen = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i])
  criteria_all$total_score_owen[i] = weighted.mean(cbsa_data, criteria_weights_owen)
}

@@

```{r student weights}
# weight criteria for students
criteria_weights_students <- c(0.18, 0.0, 0.10, 0.19, 0.17, 0.14, 0.22)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa,
         stud_EAL_total = cbsa) #this is just a place holder

@@

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$inverted_n_eal_score[i]
                  )
  criteria_all$stud_EAL_total[i] = weighted.mean(cbsa_data, criteria_weights_students)
}

@@

```{r OWEN FINAL WEIGHTS climate risk 50 and proportional weights for others}

@@

```{r climate risk 35 and Jan 31 weights from owen, eval = FALSE}

@@

criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         co2_e = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk,
         climate_EAL_risk = inverted_n_eal_score) %>% 
  mutate_if(is.numeric, ~round(., 5))

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "FINAL_total_score")
```

```{r data viz, eval = FALSE}
